Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-12-17 ms.tex
showing the pointing simulation

\subsubsection{Crosshatch Modeling}
We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
We divide the 2D Fourier power spectral density by the number of pixels in an input image.
This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
\textcolor{red}{Can we justify this more?}

@@

\subsubsection{Subpixel Crosshatching Simulation}\label{sec:CrosshatchSim}

@@

>>>>

\subsubsection{Crosshatch Pattern Modeling}
We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
We divide the 2D Fourier power spectral density by the number of pixels in an input image.
This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
\textcolor{red}{Can we justify this more?}

@@

\subsubsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}

@@

\subsubsection{Time Series Simulation}
The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointing}.

\begin{figure*}
\gridline{\fig{example_rtn.pdf}{0.45\textwidth}{Pointing Histograms} 
\fig{example_rtn.pdf}{0.45\textwidth}{Pointing Time Series} }
\caption{Pixels sometimes exhibit unusual behaviors that are not related to counting photon flux.
Examples are shown for RTN and RC pixels.
}\label{fig:tserPointing}
\end{figure*}
